MSB104_assignment1

### 2023-10-03 MSB104_assignment1.qmd
Update Rene 2
Sortert datasett på landene Finland, Tyskland og Romania per 03.10.23.

```{r}

```

>>>>

```{r}
#| label: setup
#| output: false
#| message: false
#| echo: false
library(eurostat)
library(dineq)
library(tidyverse)
library(gridExtra)
library(modelr)
library(grid)
library(ggplotify)
library(vtable)
library(dplyr)
```

# **Data Acquisition**

```{r}
#| label: Datasets
#| echo: false
library(readr)
nama_10r_3gdp <- read_delim("nama_10r_3gdp.tsv", 
    delim = "\t", escape_double = FALSE, 
    na = "NA", trim_ws = TRUE, 
    show_col_types = FALSE)

demo_r_pjanaggr3 <- read_delim("demo_r_pjanaggr3.tsv", 
    delim = "\t", escape_double = FALSE, 
    na = "NA", trim_ws = TRUE,
    show_col_types = FALSE)
```

```{r}
gdp <- nama_10r_3gdp
```

```{r}
str(gdp)
```

```{r}
countries_to_keep <- c("FI", "DE", "RO")
filtered_data <- gdp %>%
  filter(substr(`unit,geo\\time`, 9, 10) %in% countries_to_keep)
selected_columns <- filtered_data %>%
  select(`unit,geo\\time`, `2000`:`2020`)
```

```{r}
gdp_DE_FI_RO <- selected_columns 
```
